
> resume@ start /Users/me/dev/shunueda/resume
> node dist/index.js

\documentclass[letterpaper,12pt]{extarticle}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
\usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \small #2 \\
      \textit{\small #3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small #1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \small #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{
    \begin{itemize}
    \itemsep 2pt
}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------

\begin{document}

%----------HEADING----------
\begin{center}
	\textbf{\Huge \scshape Shun Ueda} \\ \vspace{1pt}
	\small (203) 979-5285 $|$ \href{mailto:me@shu.nu}{\underline{me@shu.nu}} $|$
	\href{https://www.linkedin.com/in/shunueda/}{\underline{linkedin.com/in/shunueda/}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{Lehigh University}{August 2021 -- May 2025}
{BS in Computer Science \& Engineering, BS in Mathematics}{Bethlehem, PA, United States}
\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading
{Apple}{May 2024 -- Present}
{Software Engineering Intern}{Seattle, WA, United States}
\resumeItemListStart
\resumeItem{Designed and implemented CI/CD pipelines to enhance code quality, incorporating tools for static analysis, unit testing, and code coverage.}
\resumeItem{Developed and integrated multiple features into the pipeline, increasing robustness and improving user experience.}
\resumeItemListEnd
\resumeSubheading
{Apple}{May 2023 -- August 2023}
{Software Engineering Intern}{Seattle, WA, United States}
\resumeItemListStart
\resumeItem{Designed and implemented CI/CD pipelines to enhance code quality, incorporating tools for static analysis, unit testing, and code coverage.}
\resumeItem{Developed and integrated multiple features into the pipeline, increasing robustness and improving user experience.}
\resumeItemListEnd
\resumeSubheading
{Oncospace, Inc.}{June 2022 -- August 2022}
{Software Engineering Intern}{Baltimore, MD, United States}
\resumeItemListStart
\resumeItem{Developed a cloud-based, AI-driven platform for oncologists’ treatment planning at Oncospace Inc., a Johns Hopkins Technology Ventures start-up.}
\resumeItem{Engineered a DICOM data processor for medical image visualization using cornerstone.js.}
\resumeItem{Created a Microsoft PowerApps component with a React.js frontend and C\# backend.}
\resumeItem{Implemented a CI/CD pipeline using Azure DevOps to streamline development and deployment.}
\resumeItemListEnd
\resumeSubheading
{Tech For Good Inc}{June 2021 -- August 2021}
{Software Engineering Intern}{Sharon, MA, United States}
\resumeItemListStart
\resumeItem{Managed project Mission Uplink, leading a team of 8 developers to provide internet access to schools in underdeveloped areas of Nigeria and surrounding regions.}
\resumeItem{Developed a cache-based internet access solution using Squid-cache, improving internet speed by ~600\%.}
\resumeItem{Deployed the solution on Raspberry Pi devices, utilizing AWS CodePipeline and AWS CodeDeploy to automate and streamline the deployment process.}
\resumeItem{Built a frontend application using React, TypeScript, and Node.js for deployment mapping and monitoring.}
\resumeItem{Successfully deployed 5 instances across multiple schools, significantly enhancing educational opportunities.}
\resumeItemListEnd
\resumeSubHeadingListEnd


%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
    \itemsep -2pt
	\small{\item{
		\textbf{Programming Languages}{: Java, TypeScript, Python, C++, C\#, Kotlin, SQL} \\
	}}
    \small{\item{
        \textbf{Web Technologies}{: Node.js, React.js, REST APIs} \\
	}}
    \small{\item{
        \textbf{DevOps}{: GitHub Actions, Azure DevOps, AWS (Lambda, EC2, DynamoDB, CodePipeline \& CodeDeploy), Docker} \\
	}}
    \small{\item{
        \textbf{Database Technologies}{: Postgres} \\
	}}
    \small{\item{
        \textbf{Other Skills}{: System Design, SSR, Protocol Buffers} \\
	}}
\end{itemize}

%-------------------------------------------
\end{document}

