\documentclass{resume}

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} 
\usepackage{enumitem}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Shun Ueda}
\address{+1 (203) 979–5285 \\ \href{mailto:shu225@lehigh.edu}{shu225@lehigh.edu}}

\begin{document}

\begin{rSection}{Education}
{\bf Lehigh University} \hfill { Bethlehem, PA } \\
{\bf Dual Degree} \hfill {Aug. 2021 – May. 2025 (Expected)} \\
{\emph{B.S. in Computer Science and Engineering}} \\
{\emph{B.S. in Mathematics}}
\end{rSection}

\begin{rSection}{Skills}
    \begin{itemize}
        \itemsep -5pt {} 
        \item \textbf{Programming Languages:} JavaScript/TypeScript, Java, Python, Kotlin, Scala, C/C++, SQL
        \item \textbf{Web Technologies:} Node.js, React.js (Next.js), CSS, HTML, JSON, REST
        \item \textbf{Software Development:} Object-Oriented Programming, Functional Programming, Test-Driven Development
        \item \textbf{Database Technologies:} MySQL, SQLite, Postgres, Redis, MongoDB
        \item \textbf{DevOps/CI/CD:} Git, GitHub Actions, GitLab CI/CD, Jenkins, Docker, Apache, Kubernetes, Azure DevOps
        \item \textbf{Cloud Technologies:} AWS, GCP, Firebase, Azure
        \item \textbf{Testing Tools:} Jest, JUnit, Postman, Selenium
        \item \textbf{IDEs/Code Editors:} IntelliJ IDEA, VSCode, PyCharm
    \end{itemize}
\end{rSection}

\begin{rSection}{Work Experience}

\textbf{Software Engineering Intern} \hfill May. 2023 – Aug. 2023\\
Apple Inc. \hfill \textit{Seattle, WA}
\begin{itemize}
    \itemsep -5pt {} 
     \item Developed a CI/CD pipeline for AI/ML department operations.
 \end{itemize}
 
\textbf{Software Engineering Intern} \hfill Jun. 2022 – Aug. 2022\\
Oncospace Inc. \hfill \textit{Baltimore, MD}
 \begin{itemize}
    \itemsep -5pt {} 
        \item Worked for Oncospace Inc., a Johns Hopkins Technology Ventures portfolio start-up, focused on developing a cloud-based, AI-driven platform supporting oncologists' treatment planning.
        \item Developed a Microsoft PowerApps Code component utilizing React.js and C$\#$ backend server.
        \item Orchestrated a CI/CD pipeline using Azure DevOps.
 \end{itemize}

 \textbf{Full Stack Development Intern} \hfill Nov. 2021 – May. 2022\\
Itemize \hfill \textit{Syracuse, NY}
  \begin{itemize}
     \itemsep -5pt {} 
         \item Worked for Itemize, a start-up aiming to offer a comprehensive device assurance and management system for universities.
         \item Built a dashboard using React.js, working closely with designers.
         \item Conducted code reviews and UX research.
         \item Created unit tests using Jest and established a CI/CD pipeline using GitHub Actions and Jenkins.
  \end{itemize}

  \textbf{Software Engineering Intern} \hfill June. 2021 – Aug. 2021\\
  Tech For Good Inc. \hfill \textit{Sharon, MA}
    \begin{itemize}
       \itemsep -5pt {} 
           \item Led the ”Mission Uplink” project, developing a `cache-based Internet access' system for schools without Internet access in rural Nigeria and surrounding areas.
           \item Constructed a C/C++ server software for device tracking and management.
           \item Designed a web application to visualize device locations and conditions.
           \item Participated in discussions with local school officials; deployed five devices during the internship.
           \item Led backend and frontend development, contributing 150+ commits and conducting code reviews.
    \end{itemize}


\end{rSection} 

\begin{rSection}{Academic Experience}

    \textbf{Undergraduate Researcher} \hfill Jan. 2023 – Present\\
    DAS Lab \hfill \textit{Bethlehem, PA}
    \begin{itemize}
        \itemsep -5pt {} 
         \item Conducted research at DAS Lab, under Prof.\ Eric Baumer.
         \item Developed various scrapers and text analyzers to build a dataset.
     \end{itemize}
    
      \textbf{Teaching Assistant} \hfill Aug. 2022 – Dec. 2022\\
      Lehigh University \hfill \textit{Bethlehem, PA}
        \begin{itemize}
           \itemsep -5pt {}
            \item Served as a teaching assistant for CSE 216 - Software Engineering, CSE 262 - Programming Languages 
            \item Assisted, graded, and mentored students in two advanced-level courses
        \end{itemize}
    
    \end{rSection} 

    \begin{rSection}{PROJECTS}
        \vspace{-1.25em}
        \item \textbf{aleutian} {Functional companion for JavaScript/TypeScript. it brings functional programming concepts and abstractions to the language. It provides tools and data types such as type classes, functional abstractions, and immutable data structures, enabling developers to write more declarative, composable, and type-safe code. Still under development.\hspace{1em}\href{https://github.com/shunueda/aleutian}{Source: GitHub}}
        \item \textbf{cloudcoach} {Participated in development of Cloud Coach, a training platform for Google Cloud technologies, using React.js.\hspace{1em}\href{https://cloudcoach.dev}{Access: cloudcoach.dev}}
        \item \textbf{website} {
            Website for Japanese Grace Church of New York, made with Next.js, along with Sass, and other technologies. Integrated headless CMS (prismic.io) for content management.\hspace{1em}\href{https://github.com/MegumiChurch/website}{Source: Github}\hspace{1em}\href{https://www.jgclmi.com}{Access: jgclmi.com}
        }
        \end{rSection} 

\begin{rSection}{Personal Information} 
\begin{itemize}
    \item Japanese Citizen
    \item US Lawful Permanent Resident (LPR)
\end{itemize}
\end{rSection}

\end{document}
